Nitric oxide feedback to ciliary photoreceptor cells gates a UV avoidance circuit

### 2023-06-24 Manuscript/Manuscript.Rmd
edit methods

To identify NIT-GCs, we obtained a seed database of adenylate and guanylate cyclase catalytic domains from the Pfam database (PF00211).
From these sequences, we produced a Hidden Markov Model (HMM) and used this to mine the 45 metazoan, 2 choanoflagellate and 2 filasterea species investigated.
HMM models were run in HMMR3 with an e-value of 1e−15.
We ran CD-Hit [@Fu2012] to eliminate redundant sequences (at a 80% threshold).
To identify clusters, we used sequence-similarity-based clustering in Clans [@frickey2004] and the convex-clustering option with 100 jack-knife replicates.
The NIT-GCs are extremely well conserved within the membrane-bound guanylate cyclases and form an easily recognizable cluster.
To analyze the phylogeny of NIT-GCs, the cluster containing these GCs together with membrane-bound guanylate cyclases were parsed and used for tree building.
We aligned the sequences with MAFFT version 7, with the iterative refinement method E-INS-i.
Alignments were trimmed with TrimAl in gappy-out mode [@Capella-Gutiérrez2009].
To calculate maximum-likelihood trees, we used IQ-tree2 with the LG+G4 model.
To calculate branch support, we ran 1000 replicates with the aLRT-SH-like and aBayes methods [@Minh2020].
The sequences used for the phylogenetic analysis are available in **Supplementary File 4**, the trimmed alignment is available in **Supplementary File 5** and the pre-trimmed data in **Supplementary file 6**.

@@

To measure cGMP production in a cell culture assay we used the Green cGull reporter [@Matsuda2017].
Full-length *NIT-GC1* and *NIT-GC2* coding sequences were amplified by PCR from a *Platynereis dumerilii* cDNA library and cloned into the pcDNA3.1(+) vector with the T2A self-cleaving sequence.
For the assay, COS-7 cells (Angio-proteomie, CAT no. cAP-0203) with a low endogenous level of soluble guanylate cyclase activity were used.
Cells were maintained at 37 °C in 35 mm dishes (Nunc™ Glass Bottom Dishes) containing 3 ml of DMEM, high glucose glutamax medium (Thermo; Cat. No. 10566016) supplemented with 10% fetal bovine serum (Thermo; Cat. No. 10082147).
Upon reaching approximately 85% confluency, cells were transfected with the pcDNA3.1(+)-Green-cGull-T2A-NITGC1 plasmid.
Transfections were carried out with 150 ng of each plasmid and 0.3 μl of Lipofectamine 3000 Reagent (invitrogen; Cat. No. L3000001).
Two days post-transfection, the culture medium was substituted for fresh DMEM-medium.
For single-wavelength imaging experiments, cells in 35-mm dishes were washed twice and imaged in modified Ringer's buffer (140 mM NaCl, 3.5 mM KCl, 0.5 mM NaH~2~PO~4~ , 0.5 mM S-3 MgSO~4~, 1.5 mM CaCl~2~ , 10 mM HEPES, 2 mM NaHCO~3~ and 5 mM glucose).
Dishes were mounted on a stage heated to 37 °C and imaging was done on an inverted confocal microscope (LSM880, Carl Zeiss GmbH, Jena) equipped with an oil-immersion objective lens (UApo/340, 40x, NA = 0.17).
The exposure time of the EM-CCD camera was controlled by the ZEN software (Carl Zeiss GmbH, Jena).
Images were acquired every 15 s for 10 min and stimulation was initiated 2 min after starting image acquisition.
Imaging data analysis was done with ImageJ (National Institutes of Health, Bethesda, MD, USA).
As NO donor, we used S-Nitroso-N-acetyl-D, L-penicillamine (SNAP, Sigma-Aldrich, St. Louis, MO, USA).

@@

\begin{align*}
\frac{d C_P(t)}{dt} &= 1 - \delta^{C_P} C_P(t) + K_{UV}^{C_P} UV(t) C_O(t)  + K_{G}^{C_P} G(t) , \\
\frac{dC_O(t)}{dt} &= 1 - \delta^{C_O} C_O(t) - K_{UV}^{C_O} UV(t) C_O(t), \\
\frac{dG(t)}{dt} &= 1 - \delta^{G} G(t) + K_{GC2}^G \left(1 - UV(t)\right) G(t) + K_{GC1}^G N(t) , \\
\frac{dS(t)}{dt} &= UV(t) - \frac{S(t)}{\tau_S}, \\
\frac{dC_N(t)}{dt} &= 1 - \delta^{C_N} C_N(t) + K_{S}^{C_N} S(t), \\
\frac{dN(t)}{dt} &= 1 - \delta^{N} N(t) + K_{C_N}^{N} C_N(t), \\
\frac{dC_R(t)}{dt} &= 1 - \delta^{C_R} C_R(t) - K_{S}^{C_R} S(t) + K_{C_P}^{C_R} C_P(t) - K_{C_N}^{C_R} C_N(t) C_R(t), \\
UV(t) &=
    \begin{cases}
        a, & t_{UV\: start} \leq t \leq t_{UV\: end}\\
        0, & \text{otherwise}
    \end{cases}   .
\end{align*}

The $C_P(t)$ equation describes the dynamics of the Ca^2+^ concentration in the cPRC cells.
The $K_{UV}^{C_P} UV(t) C_O(t)$ term captures the Ca^2+^ increase due to c-opsin1 activity induced by UV stimulation, while the $K_{G}^{C_P} G(t)$ term captures dependence of the Ca^2+^ dynamics on cGMP.
The $C_O(t)$ equation is added to capture the decrease of the Ca^2+^ levels observed during the UV stimulation; the mechanism of this decrease is unknown.
It could, for example, be related to the opening of the GIRK channels.
The $G(t)$ equation describes the dynamics of cGMP in the cPRC cells.
The $K_{GC1}^G N(t)$ term describes the NO-dependent increase in cGMP by NIT-GC1, while the $K_{GC2}^G \left(1 - UV(t)\right) G(t)$ term captures the cGMP decrease mediated by NIT-GC2 during UV stimulation.
The $S(t)$ describes synaptic coupling from the cPRC cells, which is assumed to act in an excitatory fashion on INNOS cells and an inhibitory fashion on INRGW cells.
This coupling is assumed to be suppressed in NIT-GC2 morphants.
The $C_N(t)$ equation describes the Ca^2+^ dynamics in the INNOS cells.
The $K_{S}^{C_N} S(t)$ term describes the Ca^2+^ increase due to the synaptic signal $S(t)$.
The $N(t)$ variable represents NO produced and secreted by the INNOS cells.
The $K_{C_N}^{N} C_N(t)$ term describes the Ca^2+^-dependent NO production within the INNOS cells.
The $C_R(t)$ equation describes the dynamics of Ca^2+^ in the INRGW cells, which depends on the other equations in a feed-forward manner.
The $K_{S}^{C_R} S(t)$ and $K_{C_N}^{C_R} C_N(t) C_R(t)$ terms describe the decrease in Ca^2+^ with respect to the synaptic signal $S(t)$ and the Ca^2+^ levels in the INNOS cells, respectively.
The $K_{C_P}^{C_R} C_P(t)$ term describes the increase in Ca^2+^ levels in the INRGW cells due to increases in the Ca^2+^ levels in the cPRC cells.
Note that all sources of Ca^2+^ variation in the INRGW cells are phenomenological in nature.
All variables have a constant (unit) production term and a linear decay rate set by the parameter $\delta_X$ where $X \in \{ C_P, C_O, G, S, C_N, C_R\}$.
Finally, the UV stimulation is described by a square pulse with amplitude $a$ and duration $t_{UV end} - t_{UV \: start}$.

@@

\begin{align*}
\frac{C_P(t)}{dt} &= 1 - \delta^{C_p} C_P(t) + K_{UV}^{C_P} UV(t) C_O(t) , \\
\frac{C_O(t)}{dt} &= 1 - \delta^{C_O} C_O(t) - K_{UV}^{C_O} UV(t) C_O(t), \\
\frac{C_R(t)}{dt} &= 1 - \delta^{C_R} C_R(t) + K_{C_P}^{C_R} C_P(t), \\
UV(t) &=
    \begin{cases}
        a, & t_{UV\: start} \leq t \leq t_{UV\: end}\\
        0, & \text{otherwise}
    \end{cases} .
\end{align*}

This reduced model eliminates the $G(t)$, $S(t)$, $C_N(t)$ and $N(t)$ variables and hence includes only c-opsin1 activity in the cPRC cells and the feedforward coupling to INRGW cells.
The synaptic signal $S(t)$ and all terms depending on it are removed due to the assumed dependence on NIT-GC2.
When the $S(t)$ input is disregarded, the activity of the INNOS cells ($C_N(t)$ and $N(t)$ variables) can be represented by a constant steady state whose values can subsequently be absorbed into all of the terms depending on these variables.
Hence these variables are eliminated in the reduced model.
Since the $K_{GC2}^G \left(1 - UV(t)\right) G(t)$ term depends directly on NIT-GC2 and when $N(t)$ is ignored the $K_{GC1}^G N(t)$ term disappears, the $G(t)$ variable can be eliminated, which consequently simplifies the $C_P(t)$ equation.
The only remaining term in $C_R(t)$ equation, $K_{C_P}^{C_R} C_P(t)$, describes feedforward coupling between the cPRC and INRGW cells.

@@

* When fitting to the cPRC data using WT or NIT-GC2 morpholino models, we eliminate the $C_R(t)$ variable since it does not have any feedback coupling with the $C_P(t)$ equation and does not affect its dynamics. When fitting to the cPRC data using the NOS-knockout model, we also eliminate the $S(t)$, $C_N(t)$ and $C_R(t)$ variables since these do not have any effect on the $C_P(t)$.
*  Set the size of the initial population to 1,000. This value provides a compromise in terms of the coverage of the parameter space and run-time of the GA.
* Set bounds of random distributions of parameters. We draw all the initial parameter values from uniform distributions over the unit interval ([0,1]). For WT condition, we fit 13 parameters, for NOS-knockout, we fit 7 parameters and for NIT-GC2 morpholino, we fit 4 parameters. 
* Evaluate the objective function on the initial population.
* Run the \texttt{gamultiobj} algorithm.
* Repeat steps 1 to 4 with bounds of parameters extended to [0,5] and using the Pareto front returned in step 4 as a part of the initial population. This step was added after observing that, although good fits to most datasets are achieved with parameter values in the interval [0,1], fits to some datasets can be improved by extending the admissible parameter range.
* Use the Euclidean norm to find the set of model parameters that best fits the data.

Since INNOS cells in the NOS-knockout condition and INRGW cells in all conditions are coupled in a feedforward manner and do not affect the 'up-stream' dynamics, we run a separate optimisation to fit data from these cells. This minimises the number of parameters that are being fitted simultaneously and ensures that the objective function is as simple as possible (using only recordings from a cell type that is being fitted). First, we fix the parameters that were found by fitting the model to the cPRC data. Next, we run the optimisation in the same way as in the case of the cPRC data but only for the parameters that pertain to dynamics that is strictly`downstream' of cPRC dynamics.

@@

* We find an inflection point that occurs after the start ($t_{UV\: start}$) of the UV stimulation. To this end, we identify the first time point $t_{AUP\: start}>t_{UV\: start}$ for which $d^2C_P(t)/dt^2=0$ and $d^2C_P(t_{k_{AUP\: start}}-1)/dt^2<d^2C_P(t_{k_{AUP\: start}})/dt^2<d^2C_P(t_{k_{AUP\: start}}+1)/dt^2$. We assume that the inflection is caused by the input from the INNOS cells.
* We then compute the $AUP$ as an integral over $C_P(t)$ starting at the inflection point and ending 125 seconds later: $AUP=\int_{t_{start}}^{t_{end}} C_P(t) dt $. To compute this, we use numerical integration via the trapezoidal method as implemented in Matlab function \texttt{trapz}. We remark that the baseline value of the $AUP$ for a Ca^2+^ profile of constant, unit value is 125.
* To capture possible variability between different cells/organisms, we compute the $AUP$ using 47 model parameter sets fitted to individual WT cPRC experimental recordings. We remove outliers, defined as being any simulated trajectories for which $C_P(t)$, after normalisation, exits the interval [0.25, 4] at any time. This $C_P(t)$ range was decided of the basis of values observed in various experiments in the lab. 
* For analysis, we use the median value of the $AUP$ at each combination of amplitude and duration.

@@

Maximum-likelihood phylogenetic tree of NOS protein sequences.** Individual branches are coloured by taxonomy. Support values are based on 1000 replicates of ultrafast bootstrap with the aLRT-SH-like and aBayes methods.

>>>>

To identify NIT-GCs, we obtained a seed database of adenylate and guanylate cyclase catalytic domains from the Pfam database (PF00211).
From these sequences, we produced a Hidden Markov Model (HMM) and used this to mine the 45 metazoan, 2 choanoflagellate and 2 filasterea species investigated.
HMM models were run in HMMR3 with an e-value of 1e−15.
We ran CD-Hit [@Fu2012] to eliminate redundant sequences (at a 80% threshold).
To identify clusters, we used sequence-similarity-based clustering in Clans [@frickey2004] and the convex-clustering option with 100 jack-knife replicates.
The NIT-GCs are extremely well conserved within the membrane-bound guanylate cyclases and form an easily recognizable cluster.
To analyze the phylogeny of NIT-GCs, the cluster containing these GCs together with membrane-bound guanylate cyclases were parsed and used for tree building.
We aligned the sequences with MAFFT version 7, with the iterative refinement method E-INS-i[@Katoh2013].
Alignments were trimmed with TrimAl in gappy-out mode [@Capella-Gutiérrez2009].
To calculate maximum-likelihood trees, we used IQ-tree2 with the LG+G4 model.
To calculate branch support, we ran 1000 replicates with the aLRT-SH-like and aBayes methods [@Minh2020].
The sequences used for the phylogenetic analysis are available in **Supplementary File 4**, the trimmed alignment is available in **Supplementary File 5** and the pre-trimmed data in **Supplementary file 6**.

@@

To measure cGMP production in a cell culture assay we used the Green cGull reporter [@Matsuda2017].
Full-length *NIT-GC1* and *NIT-GC2* coding sequences were amplified by PCR from a *Platynereis dumerilii* cDNA library and cloned into the pcDNA3.1(+) vector with the T2A self-cleaving sequence.
For the assay, COS-7 cells (Angio-proteomie, CAT no. cAP-0203) with a low endogenous level of soluble guanylate cyclase activity were used.
Cells were maintained at 37 °C in 35 mm dishes (Nunc™ Glass Bottom Dishes) containing 3 ml of DMEM, low-glucose medium (Thermo; Cat. No. 11885084) supplemented with 10% fetal bovine serum (Thermo; Cat. No. 10082147).
Upon reaching approximately 85% confluency, cells were transfected with the pcDNA3.1(+)-Green-cGull-T2A-NITGC1 plasmid.
Transfections were carried out with 150 ng of each plasmid and 0.3 μl of Lipofectamine 3000 Reagent (invitrogen; Cat. No. L3000001).
Three hours post-transfection, the culture medium was substituted for fresh DMEM-medium.
For single-wavelength imaging experiments, cells in 35-mm dishes were washed twice and imaged in modified Ringer's buffer (140 mM NaCl, 3.5 mM KCl, 0.5 mM NaH~2~PO~4~ , 0.5 mM S-3 MgSO~4~, 1.5 mM CaCl~2~ , 10 mM HEPES, 2 mM NaHCO~3~ and 5 mM glucose).
Dishes were mounted on a stage heated to 37 °C and imaging was done on an inverted confocal microscope (LSM880, Carl Zeiss GmbH, Jena) equipped with an oil-immersion objective lens (UApo/340, 40x, NA = 0.17).
The exposure time of the EM-CCD camera was controlled by the ZEN software (Carl Zeiss GmbH, Jena).
Images were acquired every 15 s for 10 min and stimulation was initiated 2 min after starting image acquisition.
Imaging data analysis was done with ImageJ (National Institutes of Health, Bethesda, MD, USA).
As NO donor, we used S-Nitroso-N-acetyl-D, L-penicillamine (SNAP, Sigma-Aldrich, St.

@@

```{=tex}
\begin{align*}
\frac{d C_P(t)}{dt} &= 1 - \delta^{C_P} C_P(t) + K_{UV}^{C_P} UV(t) C_O(t)  + K_{G}^{C_P} G(t) , \\
\frac{dC_O(t)}{dt} &= 1 - \delta^{C_O} C_O(t) - K_{UV}^{C_O} UV(t) C_O(t), \\
\frac{dG(t)}{dt} &= 1 - \delta^{G} G(t) + K_{GC2}^G \left(1 - UV(t)\right) G(t) + K_{GC1}^G N(t) , \\
\frac{dS(t)}{dt} &= UV(t) - \frac{S(t)}{\tau_S}, \\
\frac{dC_N(t)}{dt} &= 1 - \delta^{C_N} C_N(t) + K_{S}^{C_N} S(t), \\
\frac{dN(t)}{dt} &= 1 - \delta^{N} N(t) + K_{C_N}^{N} C_N(t), \\
\frac{dC_R(t)}{dt} &= 1 - \delta^{C_R} C_R(t) - K_{S}^{C_R} S(t) + K_{C_P}^{C_R} C_P(t) - K_{C_N}^{C_R} C_N(t) C_R(t), \\
UV(t) &=
    \begin{cases}
        a, & t_{UV\: start} \leq t \leq t_{UV\: end}\\
        0, & \text{otherwise}
    \end{cases}   .
\end{align*}
```
The $C_P(t)$ equation describes the dynamics of the Ca^2+^ concentration in the cPRC cells.
The $K_{UV}^{C_P} UV(t) C_O(t)$ term captures the Ca^2+^ increase due to c-opsin1 activity induced by UV stimulation, while the $K_{G}^{C_P} G(t)$ term captures dependence of the Ca^2+^ dynamics on cGMP.
The $C_O(t)$ equation is added to capture the decrease of the Ca^2+^ levels observed during the UV stimulation; the mechanism of this decrease is unknown.
It could, for example, be related to the opening of the GIRK channels.
The $G(t)$ equation describes the dynamics of cGMP in the cPRC cells.
The $K_{GC1}^G N(t)$ term describes the NO-dependent increase in cGMP by NIT-GC1, while the $K_{GC2}^G \left(1 - UV(t)\right) G(t)$ term captures the cGMP decrease mediated by NIT-GC2 during UV stimulation.
The $S(t)$ describes synaptic coupling from the cPRC cells, which is assumed to act in an excitatory fashion on INNOS cells and an inhibitory fashion on INRGW cells.
This coupling is assumed to be suppressed in NIT-GC2 morphants.
The $C_N(t)$ equation describes the Ca^2+^ dynamics in the INNOS cells.
The $K_{S}^{C_N} S(t)$ term describes the Ca^2+^ increase due to the synaptic signal $S(t)$.
The $N(t)$ variable represents NO produced and secreted by the INNOS cells.
The $K_{C_N}^{N} C_N(t)$ term describes the Ca^2+^-dependent NO production within the INNOS cells.
The $C_R(t)$ equation describes the dynamics of Ca^2+^ in the INRGW cells, which depends on the other equations in a feed-forward manner.
The $K_{S}^{C_R} S(t)$ and $K_{C_N}^{C_R} C_N(t) C_R(t)$ terms describe the decrease in Ca^2+^ with respect to the synaptic signal $S(t)$ and the Ca^2+^ levels in the INNOS cells, respectively.
The $K_{C_P}^{C_R} C_P(t)$ term describes the increase in Ca^2+^ levels in the INRGW cells due to increases in the Ca^2+^ levels in the cPRC cells.
Note that all sources of Ca^2+^ variation in the INRGW cells are phenomenological in nature.
All variables have a constant (unit) production term and a linear decay rate set by the parameter $\delta_X$ where $X \in \{ C_P, C_O, G, S, C_N, C_R\}$.
Finally, the UV stimulation is described by a square pulse with amplitude $a$ and duration $t_{UV end} - t_{UV \: start}$.

@@

```{=tex}
\begin{align*}
\frac{C_P(t)}{dt} &= 1 - \delta^{C_p} C_P(t) + K_{UV}^{C_P} UV(t) C_O(t) , \\
\frac{C_O(t)}{dt} &= 1 - \delta^{C_O} C_O(t) - K_{UV}^{C_O} UV(t) C_O(t), \\
\frac{C_R(t)}{dt} &= 1 - \delta^{C_R} C_R(t) + K_{C_P}^{C_R} C_P(t), \\
UV(t) &=
    \begin{cases}
        a, & t_{UV\: start} \leq t \leq t_{UV\: end}\\
        0, & \text{otherwise}
    \end{cases} .
\end{align*}
```
This reduced model eliminates the $G(t)$, $S(t)$, $C_N(t)$ and $N(t)$ variables and hence includes only c-opsin1 activity in the cPRC cells and the feedforward coupling to INRGW cells.
The synaptic signal $S(t)$ and all terms depending on it are removed due to the assumed dependence on NIT-GC2.
When the $S(t)$ input is disregarded, the activity of the INNOS cells ($C_N(t)$ and $N(t)$ variables) can be represented by a constant steady state whose values can subsequently be absorbed into all of the terms depending on these variables.
Hence these variables are eliminated in the reduced model.
Since the $K_{GC2}^G \left(1 - UV(t)\right) G(t)$ term depends directly on NIT-GC2 and when $N(t)$ is ignored the $K_{GC1}^G N(t)$ term disappears, the $G(t)$ variable can be eliminated, which consequently simplifies the $C_P(t)$ equation.
The only remaining term in $C_R(t)$ equation, $K_{C_P}^{C_R} C_P(t)$, describes feedforward coupling between the cPRC and INRGW cells.

@@

-   When fitting to the cPRC data using WT or NIT-GC2 morpholino models, we eliminate the $C_R(t)$ variable since it does not have any feedback coupling with the $C_P(t)$ equation and does not affect its dynamics. When fitting to the cPRC data using the NOS-knockout model, we also eliminate the $S(t)$, $C_N(t)$ and $C_R(t)$ variables since these do not have any effect on the $C_P(t)$.
-   Set the size of the initial population to 1,000. This value provides a compromise in terms of the coverage of the parameter space and run-time of the GA.
-   Set bounds of random distributions of parameters. We draw all the initial parameter values from uniform distributions over the unit interval ([0,1]). For WT condition, we fit 13 parameters, for NOS-knockout, we fit 7 parameters and for NIT-GC2 morpholino, we fit 4 parameters.
-   Evaluate the objective function on the initial population.
-   Run the \texttt{gamultiobj} algorithm.
-   Repeat steps 1 to 4 with bounds of parameters extended to [0,5] and using the Pareto front returned in step 4 as a part of the initial population. This step was added after observing that, although good fits to most datasets are achieved with parameter values in the interval [0,1], fits to some datasets can be improved by extending the admissible parameter range.
-   Use the Euclidean norm to find the set of model parameters that best fits the data.

Since INNOS cells in the NOS-knockout condition and INRGW cells in all conditions are coupled in a feedforward manner and do not affect the 'up-stream' dynamics, we run a separate optimisation to fit data from these cells.
This minimises the number of parameters that are being fitted simultaneously and ensures that the objective function is as simple as possible (using only recordings from a cell type that is being fitted).
First, we fix the parameters that were found by fitting the model to the cPRC data.
Next, we run the optimisation in the same way as in the case of the cPRC data but only for the parameters that pertain to dynamics that is strictly\`downstream' of cPRC dynamics.

@@

-   We find an inflection point that occurs after the start ($t_{UV\: start}$) of the UV stimulation. To this end, we identify the first time point $t_{AUP\: start}>t_{UV\: start}$ for which $d^2C_P(t)/dt^2=0$ and $d^2C_P(t_{k_{AUP\: start}}-1)/dt^2<d^2C_P(t_{k_{AUP\: start}})/dt^2<d^2C_P(t_{k_{AUP\: start}}+1)/dt^2$. We assume that the inflection is caused by the input from the INNOS cells.
-   We then compute the $AUP$ as an integral over $C_P(t)$ starting at the inflection point and ending 125 seconds later: \$AUP=\int*{t*{start}}\^{t\_{end}} C_P(t) dt \$. To compute this, we use numerical integration via the trapezoidal method as implemented in Matlab function \texttt{trapz}. We remark that the baseline value of the $AUP$ for a Ca^2+^ profile of constant, unit value is 125.
-   To capture possible variability between different cells/organisms, we compute the $AUP$ using 47 model parameter sets fitted to individual WT cPRC experimental recordings. We remove outliers, defined as being any simulated trajectories for which $C_P(t)$, after normalisation, exits the interval [0.25, 4] at any time. This $C_P(t)$ range was decided of the basis of values observed in various experiments in the lab.
-   For analysis, we use the median value of the $AUP$ at each combination of amplitude and duration.

@@

Maximum-likelihood phylogenetic tree of NOS protein sequences.\*\* Individual branches are coloured by taxonomy.
Support values are based on 1000 replicates of ultrafast bootstrap with the aLRT-SH-like and aBayes methods.
